
\title{Spin Model Checker}
%\author{}
\date{}

\begin{document}

\section{Installation}
%First download the source code from
%\url{http://spinroot.com/spin/Src/index.html}

What follows are copy-pasteable commands to make \ilcode{spin} and \ilcode{ispin} valid commands.
To copy and paste: highlight the commands, middle click in a terminal, and hit enter so the last command is executed too.

Download, build, and set up \ilname{spin}, do the following.
(Change \ilcode{pkg=spin645.tar.gz} to reflect the current version number.)
\begin{code}
bash
pkg=spin645.tar.gz
mkdir -p "$HOME/bin"
mkdir -p "/tmp/ccspin-$USER"
cd "/tmp/ccspin-$USER"
wget http://spinroot.com/spin/Src/$pkg
tar xf $pkg
cd Spin/Src*
make
cp -f spin "$HOME/bin/spin"
cp -f ../iSpin/ispin.tcl "$HOME/bin/ispin"
cd "$HOME/bin"
rm -r "/tmp/ccspin-$USER"
chmod +x spin ispin
mkdir -p spinshare
curl 'https://raw.githubusercontent.com/grencez/protocon/master/s/{spinsafe,spinlive,spinltl,spinplay,spinshare/spinclude.sh}' -o '#1'
chmod +x spinsafe spinlive spinltl spinplay
exit
\end{code}

\section{Path Setup}

Finally, you might need to set up your path to include \ilfile{~/bin/}.
Run the following:
\begin{code}
echo "${PATH}" | grep -o -e "$HOME/bin" | sed -e 's/^.*$/All is well!/'
\end{code}
If it prints \ilcode{All is well!}, then your installation is finished.
Otherwise, continue reading.

If you use the \ilname{bash} shell run the following:
\begin{code}
echo 'export PATH=$HOME/bin:$PATH' >> $HOME/.bashrc
\end{code}
If you use the \ilname{tcsh} shell or don't know (it's the default shell at Michigan Tech), run the following:
\begin{code}
bash
echo 'setenv PATH "${HOME}/bin:${PATH}"' >> $HOME/.cshrc
exit
\end{code}
The changes may not take effect unless you log out and log in again.
But after that, the commands \ilcode{spin}, \ilcode{ispin}, \ilcode{spinsafe}, \ilcode{spinlive}, and \ilcode{spinltl} should work!

\section{Vim Settings}

If you use Vim, the following will set up indentation and syntax.
\begin{code}
bash
mkdir -p ~/.vim
cd ~/.vim
mkdir -p indent syntax
wget cs.mtu.edu/~apklinkh/drop/vim-promela.tar.gz
tar xf vim-promela.tar.gz
rm vim-promela.tar.gz
cp -t indent vim-promela/indent/promela.vim
cp -t syntax vim-promela/syntax/promela.vim
rm -r vim-promela
echo 'autocmd BufNewFile,BufRead *.pml set ft=promela sw=2 ts=2' >> filetype.vim
exit
\end{code}

If you don't have a \ilfile{~/.vimrc} already, this will make it:
\begin{code}
bash
cd "$HOME"
echo 'set nocompatible' >> .vimrc
echo 'filetype on' >> .vimrc
echo 'filetype plugin indent on' >> .vimrc
echo 'syntax enable' >> .vimrc
exit
\end{code}

If you have no idea what's going on with this editor:
\begin{code}
vimtutor
\end{code}

\end{document}

