
\title{QEMU Notes}
\date{}

\begin{document}

\tableofcontents

\textbf{In progress.}

\begin{code}
qemu-kvm -snapshot -display vnc=:2 Metasploitable.vmdk
\end{code}

\begin{code}
qemu-img create -f qcow2 windows-dev.img 100G
qemu-system-i386 -hda windows-dev.img -cdrom xp-installer.img -boot d
qemu-system-i386 -m 1G -net nic,model=rtl8139 -net user -hda windows-dev.img
\end{code}

\section{Resize a VMDK Image}
(1) Convert to raw
\begin{code}
qemu-img convert -f vmdk orig.vmdk -O raw orig.raw
\end{code}
(2) Create an empty raw image
\begin{code}
qemu-img create -f raw temp.raw 100M
\end{code}
(3) Combine
\begin{code}
cat orig.raw tmp.raw > resized.raw
\end{code}
(4) Convert back to original format
\begin{code}
qemu-img convert -f raw resized.raw -O vmdk resized.vmdk
\end{code}

\section{Mount Image}
\begin{code}
sudo modprobe nbd
\end{code}
First partition
\begin{code}
sudo qemu-nbd -c /dev/nbd1 -P1 windows-dev.img
\end{code}
Mount it
\begin{code}
sudo mount /dev/nbd1 /mnt/WIND
\end{code}


\section{Resize QCOW Image}
Variables used!
\begin{code}
img_a=windows-dev.img
img_b=/mnt/FIRE/vm/windows-dev-P1.img
dev_a=/dev/nbd1
dd_blocksz=16M
\end{code}
size you want the filesystem to be (base 10)
\begin{code}
size=21G
# max size of qemu image (base 2... I don't know how to make it consistent)
\begin{code}
max_size=21G
\end{code}

Need to ensure the network block device module is available.
\begin{code}
sudo modprobe nbd
\end{code}
Associate the first partition of your image with a network block device.
\begin{code}
sudo qemu-nbd -c $dev_a -P1 $img_a
\end{code}
Resize file system
\begin{code}
sudo ntfsresize -s $size $dev_a
\end{code}

\section{Create New Image}
\begin{code}
qemu-img create -f qcow2 $img_b 1
sudo qemu-nbd -c $dev_b $img_b
\end{code}
Set up partitions, ensure the starting offsets are the same as in \ilcode{$img_a}.
\begin{code}
sudo fdisk $dev_b
sudo qemu-nbd -c $dev_b -P1 $img_b
\end{code}

Resize the partition.
We have to first associate the network block device with the whole image.
\begin{code}
sudo qemu-nbd -d $dev_a
sudo qemu-nbd -c $dev_a $img_a
\end{code}
Edit the partition table (you can use GParted instead of fdisk).
\begin{code}
sudo fdisk $dev_a
\end{code}
Be sure to keep the start offset the same.
If it's giving 2048 instead of 63, you need the DOS label.
Re-associate only the first partition with the network block device.
\begin{code}
sudo qemu-nbd -d $dev_a
sudo qemu-nbd -c $dev_a -P1 $img_a
\end{code}

Copy the partition to a temporary location.
\begin{code}
sudo dd if=$dev_a of=$dev_b conv=count_bytes bs=$dd_blocksz count=${size}B
\end{code}

Create a new image
\begin{code}
sudo qemu-nbd -d $dev_a
rm $img_a
qemu-img create -f qcow2 $img_a 40G
\end{code}
Set up its partition table properly.
\begin{code}
sudo qemu-nbd -c $dev_a $img_a
sudo fdisk $dev_a
sudo qemu-nbd -d $dev_a $img_a
\end{code}


\end{document}

